\emph{BattleTech: Outworlds Wastes} is designed to support both BattleTech and Alpha Strike.
If the event or league supports both rule systems, then your force must be within all of the BV and PV limits given.
If the event or league will only use BattleTech, then your force only needs to be within the BV limits given, or only within the PV limits for Alpha Strike.

\emph{BattleTech: Outworlds Wastes} is designed for full combined arms play using \emph{BattleTech: Total Warfare} rules; however organizers may use the Battlefield Support: Asset rules from the the \emph{BattleTech: Mercenaries} box set instead.
There are three common combinations of rules that a league or event may use.

\begin{itemize}

  \item {\bfseries Total Warfare}: Use the force construction rules as written.
    Use \emph{BattleTech: Total Warfare} rules for non-'Mech units.
    Use Battlefield Support: Strikes rules from the \emph{BattleTech: Mercenaries} box set.
    Aerospace and artillery units may also use \emph{BattleTech: Total Warfare} rules.

  \item {\bfseries Force Assets}: Use the force construction rules as written.
    Use Battlefield Support: Assets rules from the \emph{BattleTech: Mercenaries} bot set for non-'Mech units.
    You may only use Battlefield Support: Assets from your force during play, but Assets cannot score objectives.
    Use Battlefield Support: Strikes rules from the \emph{BattleTech: Mercenaries} box set.
    In order to use Battlefield Support: Strikes, your command must have a unit capable of offering the support.

  \item {\bfseries Hired Assets}: For Event Play, you may start with 3,000 BV (100 PV) of 'Mech units; do not add non-'Mech units to your force.
    For League Play, you may start with 9,000 BV (300 PV) of 'Mech units; do not add non-'Mech units to your force.
    Use Battlefield Support: Assets rules from the \emph{BattleTech: Mercenaries} bot set for non-'Mech units.
    You may add any Battlefield Support: Assets to your force, up to the BSP limit for the scenario, but Assets cannot score objectives.
    Use Battlefield Support: Strikes rules from the \emph{BattleTech: Mercenaries} box set.
    You may use any Battlefield Support: Strikes and your force should not contain these supporting non-'Mech units.

\end{itemize}
